---
title: "Investigate data AACES2 Cases Controls"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   margin-bottom: 25;
}

table {
    margin-top: 25px;
    margin-bottom: 10px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary_print_engine = "gt")
# options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row_padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Association between pre-diagnostic inflammatory-related exposures and immune cell abundance in cases controls population</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
library(data.table)
library(nnet)
library(gtsummary)
library(survival)
library(survminer)
library(mclust)
library(gplots)
```


```{r load}
ROI_global <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_case_ctrl_AACES_NCOCS/ROI_global.rds")
markers_ROI <- readRDS("/Users/colinccm/Documents/GitHub/Peres/IF_case_ctrl_AACES_NCOCS/markers_ROI.rds")

# Remove these IDs from whole data because 2 are NAs in BMI and 2 are there matched
# remove_id_bmi <- paste0(c("45142", "45809", "181810", "42204"), collapse = "|")

# # Remove these IDs from peripheral ROI because 2 are NAs and 2 are there matched
# remove_id <- paste0(c("110318", "43220", "42774", "46619"), collapse = "|")
```

I removed 4 patients who don't have intratumoral ROI in the new AACES date
```{r remove patients}
# Remove these IDs with no intratumoral ROI
remove_id <- paste0(c("110362", "161094", "190155", "190176"), collapse = "|")


ROI_global <- ROI_global %>% 
  filter(site == "AAS") %>% 
  filter(!str_detect(suid, remove_id))

markers_ROI <- markers_ROI %>% 
  filter(site == "AAS") %>%
  filter(!str_detect(suid, remove_id))
```
<br>
<br>

***

`r emo::ji("spiral_notepad")` WHAT IS THE DEFINITION FOR ADJ, NEO, DBLSTKSTAT??


# I. Data exploration
## 1. Patient characteristics
```{r patient table}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(refage, refage_cat, stage, BMI_recent, BMI_recent_grp,
        smoker, diab, histology,
         dblkstat_treat, neoadj_treat, adj_treat
         ) %>% 
  tbl_summary(
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              label = list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
                           dblkstat_treat ~ "Debulking Status", 
                           adj_treat ~ "Adjuvant chemotherapy", neoadj_treat ~ "Neodjuvant chemotherapy",
                           smoker ~ "Smoking status"),
              type = list(c(diab, dblkstat_treat, adj_treat, neoadj_treat) ~ "categorical"),
              digits = list(all_continuous() ~ 1)) %>%
      modify_header(list(label ~ "**Patient characteristics**")) %>% 
  bold_labels()
```

# 2. Distribution of the potential inflammatory-related pre-diagnostic exposures in the overall study population, by race, and by immune abundance (only use overall intratumoral and overall peritumoral), immune signatures, and immunoscore

## Summary table
```{r exposures table}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(BMI_recent_grp, BMI_YA_grp, diab,
         smokever, smokcurrent,
         packyrs, packyrs_cat, talcever, talcgen, talcnongen,
         aspirin, NSAID,aceta, hyster, hyster1yr,
         hyster2yr, hystertype,
         tubelig, endomet, fibroids,
         pid, education,
         married, 
         anyfhever, anyfhdur, anyfhdur_cat,
         race) %>% 
  tbl_summary(
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # label = list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
              #              dblkstat_treat ~ "Debulking Status", adj_treat ~ "Adjuvant chemotherapy",
              #              smoker ~ "Smoking status"),
              type = list(c(diab,
                talcever, talcgen, talcnongen,
                            aspirin, NSAID,aceta, 
                            hyster, hyster1yr,
                            hyster2yr, hystertype,
                            tubelig, endomet, fibroids,
                            pid, education, anyfhever,
                            married) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  modify_header(list(label ~ "**Patient Exposure characteristics**")) %>% 
  bold_labels()
```

## Intratumoral cd3 total
```{r}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(BMI_recent_grp, BMI_YA_grp, diab,
         smokever, smokcurrent,
         packyrs, packyrs_cat, talcever, talcgen, talcnongen,
         aspirin, NSAID,aceta, hyster, hyster1yr,
         hyster2yr, hystertype,
         tubelig, endomet, fibroids,
         pid, education,
         married, 
         anyfhever, anyfhdur, anyfhdur_cat, cd3_total_i) %>% 
  tbl_summary(by = cd3_total_i,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              type = list(c(diab,
                talcever, talcgen, talcnongen,
                            aspirin, NSAID,aceta,
                            hyster, hyster1yr,
                            hyster2yr, hystertype,
                            tubelig, endomet, fibroids,
                            pid, education, anyfhever,
                            married) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

## Intratumoral cd3cd8 total
```{r}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(BMI_recent_grp, BMI_YA_grp, diab,
         smokever, smokcurrent,
         packyrs, packyrs_cat, talcever, talcgen, talcnongen,
         aspirin, NSAID,aceta, hyster, hyster1yr,
         hyster2yr, hystertype,
         tubelig, endomet, fibroids,
         pid, education,
         married, 
         anyfhever, anyfhdur, anyfhdur_cat, cd3plus_cd8plus_total_i) %>% 
  tbl_summary(by = cd3plus_cd8plus_total_i,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              type = list(c(diab,
                talcever, talcgen, talcnongen,
                            aspirin, NSAID,aceta,
                            hyster, hyster1yr,
                            hyster2yr, hystertype,
                            tubelig, endomet, fibroids,
                            pid, education, anyfhever,
                            married) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

## Intratumoral Immunoscore
```{r}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(BMI_recent_grp, BMI_YA_grp, diab,
         smokever, smokcurrent,
         packyrs, packyrs_cat, talcever, talcgen, talcnongen,
         aspirin, NSAID,aceta, hyster, hyster1yr,
         hyster2yr, hystertype,
         tubelig, endomet, fibroids,
         pid, education,
         married, 
         anyfhever, anyfhdur, anyfhdur_cat, immunoscore_2018lancet_patients) %>% 
  tbl_summary(by = immunoscore_2018lancet_patients,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              type = list(c(diab,
                talcever, talcgen, talcnongen,
                            aspirin, NSAID,aceta,
                            hyster, hyster1yr,
                            hyster2yr, hystertype,
                            tubelig, endomet, fibroids,
                            pid, education, anyfhever,
                            married) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

## Violin plots
```{r violin}
# for (j in marker_var){
#
#   for (i in exposure_var){
#     p1 <- markers_ROI %>%
#       ggplot()+
#       geom_violin(aes(x=i, y=total_percent_cd3_i), scale = "count")+
#       geom_boxplot(aes(x=i, y=total_percent_cd3_i), width=.1) +
#       theme_classic2()+
#       labs(x=NULL, y=NULL, title="Intratumoral \nROIs")
#     p2 <- markers_ROI %>%
#       ggplot()+
#       geom_violin(aes(x=i, y=j), scale = "count")+
#       geom_boxplot(aes(x=i, y=j), width=.1) +
#       theme_classic2()+
#       labs(x=NULL, y=NULL, title="Peripheral \nROIs")
#
#     gridExtra::grid.arrange(p1, p2, ncol = 2,
#                             top = "% of Cells Present in", left =  paste("Overall", markers_ROI[[i]], "immune cells (%) per patients"),
#                             bottom = "Data on Race-Matched Patients")
#   }
# }

exposure_var <- c("BMI_recent_grp", "BMI_YA_grp", "diab",
                  "smokever", "smokcurrent",
                  "packyrs", "packyrs_cat", "talcever", "talcgen", "talcnongen",
                  "aspirin", "NSAID", "aceta", "hyster1yr",
                  "hyster2yr", "hystertype",
                  "tubelig", "endomet", "fibroids",
                  "pid", "education",
                  "married", "anyfhever", "anyfhdur", "anyfhdur_cat") 
marker_var <- c("total_percent_cd3_i", "total_percent_cd3plus_cd8plus_i", 
                "total_percent_cd3plus_foxp3plus_i", "total_percent_cd11b_i", 
                "total_percent_cd11bplus_cd15plus_i",
                "total_percent_cd3_p", "total_percent_cd3plus_cd8plus_p", 
                "total_percent_cd3plus_foxp3plus_p", "total_percent_cd11b_p", 
                "total_percent_cd11bplus_cd15plus_p")

violin_plot <- function(data, type){

  for (i in exposure_var){

    if(class(markers_ROI[[i]]) == "factor" | class(markers_ROI[[i]]) == "character") {

      p1 <- markers_ROI %>%
        ggplot()+
        geom_violin(aes(x=.data[[i]], y= .data[[paste0(type, "_i")]]), scale = "count")+
        geom_boxplot(aes(x=.data[[i]], y= .data[[paste0(type, "_i")]]), width=.1) +
        theme_classic2()+
        labs(x=NULL, y=NULL, title="Intratumoral \nROIs")
      p2 <- markers_ROI %>%
        ggplot()+
        geom_violin(aes(x=.data[[i]], y= .data[[paste0(type, "_p")]]), scale = "count")+
        geom_boxplot(aes(x=.data[[i]], y= .data[[paste0(type, "_p")]]), width=.1) +
        theme_classic2()+
        labs(x=NULL, y=NULL, title="Peripheral \nROIs")

      main <- str_match(type, "percent_(.*)$")[,2]
      gridExtra::grid.arrange(p1, p2, ncol = 2,
                              top = "% of Cells Present in",
                              left =  paste("Overall", main, "immune cells (%) per patients"),
                              bottom = "Data on Race-Matched Patients")
    }
  }
}

violin_plot(data = markers_ROI, type = "total_percent_cd3")
violin_plot(data = markers_ROI, type = "total_percent_cd3plus_cd8plus")
violin_plot(data = markers_ROI, type = "total_percent_cd3plus_foxp3plus")
violin_plot(data = markers_ROI, type = "total_percent_cd11b")
violin_plot(data = markers_ROI, type = "total_percent_cd11bplus_cd15plus")
```

## Scatter plots
```{r point}
# markers_ROI %>%
#         ggplot(aes(x=.data[[i]], y= .data[[paste0("percent_cd3_total", "_i")]]))+
#   geom_point()+
#   geom_smooth(method = "lm", se = FALSE) +
# stat_regline_equation(label.y.npc = 1)+
#         # geom_violin(aes(x=.data[[i]], y= .data[[paste0("percent_cd3_total", "_i")]]), scale = "count")+
#         # geom_boxplot(aes(x=.data[[i]], y= .data[[paste0("percent_cd3_total", "_i")]]), width=.1) +
#         theme_classic2()+
#         labs(x=NULL, y=NULL, title="Intratumoral \nROIs")


point_plot <- function(data, type){

  for (i in exposure_var){

    if(class(markers_ROI[[i]]) == "numeric" | class(markers_ROI[[i]]) == "integer") {

      p1 <- markers_ROI %>%
        ggplot(aes(x=.data[[i]], y= .data[[paste0(type, "_i")]]))+
        geom_point()+
        geom_smooth(method = "lm", se = FALSE)+
        stat_regline_equation(label.y.npc = 1)+
        theme_classic2()+
        labs(y=NULL, title="Intratumoral \nROIs")
      p2 <- markers_ROI %>%
        ggplot(aes(x=.data[[i]], y= .data[[paste0(type, "_p")]]))+
        geom_point()+
        geom_smooth(method = "lm", se = FALSE)+
        stat_regline_equation(label.y.npc = 1)+
        theme_classic2()+
        labs(y=NULL, title="Peripheral \nROIs")

      main <- str_match(type, "percent_(.*)$")[,2] %>%
        str_remove(., "_")
      gridExtra::grid.arrange(p1, p2, ncol = 2,
                              top = "% of Cells Present in",
                              left =  paste("Overall", main, "immune cells (%) per patients"),
                              bottom = "Data on Race-Matched Patients")
    }
  }
}
point_plot(data = markers_ROI, type = "total_percent_cd3")
point_plot(data = markers_ROI, type = "total_percent_cd3plus_cd8plus")
point_plot(data = markers_ROI, type = "total_percent_cd3plus_foxp3plus")
point_plot(data = markers_ROI, type = "total_percent_cd11b")
point_plot(data = markers_ROI, type = "total_percent_cd11bplus_cd15plus")
```
<br>
<br>

***
***

<br>

# Logistic regression adjusted by age + stage

```{r log reg function}
exp_var <- c("BMI_recent_grp", "bmi_recent5", "BMI_YA_grp", "diab",
             "smokever", "smokcurrent",
             "packyrs", "packyrs_cat", "talcever", "talcgen", "talcnongen",
             "aspirin", "NSAID", "aceta", "hyster1yr",
             "hyster2yr", "hystertype",
             "tubelig", "endomet", "fibroids",
             "pid", "education",
             "married", "anyfhever", "anyfhdur", "anyfhdur_cat") 

loreg_table_int <- function(data, type){
  
  for (i in exp_var){
    
    main <- str_match(type, "(.*)_total")[,2] %>% 
      str_remove(., "_")
    
    tbl1 <- glm(data[[paste0(type, "_i")]] ~ data[[i]] + refage + stage, 
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE, 
                           label = list(`data[[i]]` ~ i)) %>% 
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)
    
  }
}

loreg_table_per <- function(data, type){

  for (i in exp_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl2 <- glm(data[[paste0(type, "_p")]] ~ data[[i]] + refage + stage, 
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Peripheral"))
    print(tbl2)

  }
}
```

### cd3_total

<div class = "row">
<div class = "col-md-6">
```{r log reg intra, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "cd3_total")
```
</div>

<div class = "col-md-6">
```{r log reg periph, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "cd3_total")
```
</div>
</div>

***

### cd3_cd8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "cd3plus_cd8plus_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "cd3_cd8_total")
```
</div>
</div>

***

### cd3_foxp3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "cd3plus_foxp3plus_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "cd3_foxp3_total")
```
</div>
</div>

***

### cd11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "cd11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "cd11b_total")
```
</div>
</div>

***

### cd11b_cd15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "cd11bplus_cd15plus_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "cd11b_cd15_total")
```
</div>
</div>

<br>

***

<br>

# Immunoscore 3 cat 2018lancet

```{r multi reg function}
multinom_pivot_wider <- function(x) {
  # check inputs match expectatations
  if (!inherits(x, "tbl_regression") || !inherits(x$model_obj, "multinom")) {
    stop("`x=` must be class 'tbl_regression' summary of a `nnet::multinom()` model.")
  }

  # create tibble of results
  df <- tibble::tibble(outcome_level = unique(x$table_body$groupname_col))
  df$tbl <-
    purrr::map(
      df$outcome_level,
      function(lvl) {
        gtsummary::modify_table_body(
          x,
          ~dplyr::filter(.x, .data$groupname_col %in% lvl) %>%
            dplyr::ungroup() %>%
            dplyr::select(-.data$groupname_col)
        )
      }
    )

  tbl_merge(df$tbl, tab_spanner = paste0("**", df$outcome_level, "**"))
}

multireg_table_int <- function(data){

  for (i in exp_var){

    tbl1 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + stage,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider() #%>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Intratumoral"))
    print(tbl1)

  }
}

multireg_table_per <- function(data, type){

  for (i in exp_var){

    tbl2 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + stage,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider()# %>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Peripheral"))
    print(tbl2)

  }
}
```

### Intratumoral

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
multireg_table_int(data = markers_ROI_black)
```
</div>

### Peripheral

<div class = "col-md-6">
```{r, results = 'asis'}
multireg_table_per(data = markers_ROI_black)
```
</div>
</div>

<br>

***


