---
title: "TAM_TMA survival analysis using marker cutpoint to categorize macrophage types"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```


```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(survival)
library(survminer)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
tam_data <- 
  read_rds(paste0(here::here(),
                  "/Clean_mapped_macrophage_data_long_format_with_cat_09282023.rds"))
clinical <- 
  read_rds(paste0(here::here(),
                  "/case_ctrl_data_07132023.rds"))
tx_data_aaces <- 
  read_rds(paste0(here::here(),
                  "/AACES_tx_12082020.rds"
  )) %>% 
  mutate(dblkstat_CA125 = case_when(
    dblkstat_CA125 == 1                  ~ "optimal debulking",
    dblkstat_CA125 == 2                  ~ "suboptimal debulking",
    dblkstat_CA125 == 99                 ~ NA_character_
  ))
```

```{r prep data}
tam_data <- left_join(tam_data %>% 
                         mutate(suid = as.character(suid)),
                      clinical,
                      by = "suid") %>% 
  # Remove patients that have to be excluded for AACES
  filter(!is.na(OCWAAID)) %>% 
  # Add debulking status
  left_join(., tx_data_aaces %>% 
              mutate(suid = as.character(suid)),
                      by = "suid")

compartment_type <- "Tumor"
tam_data <- tam_data %>% 
  filter(compartment == compartment_type)
```

```{r label}
var_label(tam_data) <-
  list(refage = "Patient Age", refage_cat = "Patient Age - Categories",
       stage_cat = "Stage", histology = "Histology",
       grade = "Grade", dblkstat_CA125 = "Debulking Status",
       neutral_3070p = "Neutrals at 30/70", m1_70p = "M1 at 30/70",
       m2_30p = "M2 at 30/70", neutral_4060p = "Neutrals at 40/60",
       m1_60p = "M1 at 40/60", 
       m2_40p = "M2 at 40/60",
       neutral_3070p_cat = "Neutrals at 30/70 categories", m1_70p_cat = "M1 at 30/70 categories",
       m2_30p_cat = "M2 at 30/70 categories", neutral_4060p_cat = "Neutrals at 40/60 categories",
       m1_60p_cat = "M1 at 40/60 categories", 
       m2_40p_cat = "M2 at 40/60 categories"
  )
```

<br>

***
<span style="color: steelblue; font-size: 40px;">Focus on `r compartment_type` compartment</span>

***
<br>

# I. Table 1. Patient characteristics overall

```{r}
tam_data %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(refage, refage_cat, 
         race, grade, dblkstat_CA125,
         stage_cat, histology,
         histotype1, histotype2) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # label = list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
              #              stage ~ "Stage", histology ~ "Histology"
              #              # dblkstat_CA125 ~ "Debulking Status", adj ~ "Adjuvant chemotherapy",
              #              ),
              digits = list(all_continuous() ~ 1)) %>%
      modify_header(list(label ~ "**Patient characteristics**"#, all_stat_cols() ~ "**{level}**, N = {n}"
                    )) %>%
  bold_labels()
```

* Note :  
  * Calculation is restricted to CD68+ cells (TAM)  
  * Starting from this restricted per cell data, Alex calculated a log10 of the index M1:M2 using  

  $$
  M1:M2\ index= \frac{CD86\ Cytoplasm\ Intensity\ \times PSTAT1\ Nuclear\ Intensity}{CD206\ Cytoplasm\ Intensity\ \times CD163\ Cytoplasm\ Intensity}
  $$

  * M1 - Neutrals - M2 are then categorized using quantile cut-points (2 different cut-points were tested - quantile 70/30 or 60/40)  
    * If log10(M1:M2 index) > quantile 0.7 or 0.6 (aka more M1 markers), the cell is identified as M1 (pro-inflammatory anti-tumoral macrophages)  
    * If log10(M1:M2 index) < quantile 0.3 or 0.4 (aka more M1 markers), the cell is identified as M2 (are )anti-inflammatory pro-tumoral macrophages (proliferation))  
    * Cells that have log10(M1:M2 index) between quantiles 0.7-0.3 (or 0.6-0.4) are Neutrals cells. Mary showed me that the cells classified as Neutrals with this approach and the same cells classified as M0 using the simple classification (presence or absence of M1 or M2 markers) have a 0.81 correlation coefficient (r)  

# Analysis using averaged cores
# II. TAM characteristic - focus on `r compartment_type` compartment
```{r cleaning}
tam_data %>%
  select(m1_70p : neutral_4060p,
         m1_70p_cat : neutral_4060p_cat) %>%
  tbl_summary()
```

```{r}
tam_data %>%
  select(m1_70p : neutral_4060p) %>%
  pivot_longer(cols = everything(),
               names_to = "cell_type") %>%
  mutate(cell_type =
           factor(cell_type,
                  levels = c("neutral_3070p", "m1_70p",
                             "m2_30p", "neutral_4060p",
                             "m1_60p", "m2_40p"))) %>%
  ggplot(aes(x= cell_type, y= value))+
  geom_violin()+
  scale_y_log10()+
  coord_flip()

tam_data %>%
  select(suid, m1_70p : neutral_3070p) %>%
  pivot_longer(cols = -suid,
               names_to = "cell_type") %>%
  mutate(cell_type =
           factor(cell_type,
                  levels = c("neutral_3070p", "m1_70p",
                             "m2_30p"))) %>%
  ggpaired(x = "cell_type", y = "value", id = "suid",
           color = "cell_type", line.color = "gray", line.size = 0.4, point.size = 0,
           palette = "jco")+
  scale_y_log10()+
  coord_flip()

tam_data %>%
  select(suid, m1_60p : neutral_4060p) %>%
  pivot_longer(cols = -suid,
               names_to = "cell_type") %>%
  mutate(cell_type =
           factor(cell_type,
                  levels = c("neutral_4060p",
                             "m1_60p", "m2_40p"))) %>%
  ggpaired(x = "cell_type", y = "value", id = "suid",
           color = "cell_type", line.color = "gray", line.size = 0.4, point.size = 0,
           palette = "jco")+
  scale_y_log10()+
  coord_flip()
```

# III. HR non adjusted by debulking status
## 1. Adjusted HR - continuous
```{r}
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_3070p + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_70p + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_30p + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_4060p + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_60p + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_40p + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

## 2. Adjusted HR - categories
```{r}
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_3070p_cat + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_70p_cat + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_30p_cat + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_4060p_cat + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_60p_cat + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_40p_cat + refage + stage_cat + histotype2,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

# IV. Adjusted by debulking status
## 1. Adjusted HR - continuous
```{r}
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_4060p + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_60p + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_40p + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_3070p + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_70p + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_30p + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

## 2. Adjusted HR - categories
```{r}
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_4060p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_60p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_40p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ neutral_3070p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_70p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_30p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```
<br>

***

# V. KM
```{r}
ggsurvplot(survfit(Surv(os_time, os_event) ~ m2_40p_cat,
                   data=tam_data),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "M2 at 40p cutpoint categories",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```
<br>
<br>

***
<br>

# Analysis using all cores
```{r load cores}
core_data <-
  read_rds(paste0(here::here(),
                  "/Clean_mapped_macrophage_bycore_data_long_format_with_cat_09282023.rds"))
```

```{r prep cores}
core_data <- left_join(core_data %>%
                         mutate(suid = as.character(suid)),
                      clinical,
                      by = "suid") %>%
  # Remove patients that have to be excluded for AACES
  filter(!is.na(OCWAAID)) %>%
  # Add debulking status
  left_join(., tx_data_aaces %>%
              mutate(suid = as.character(suid)),
                      by = "suid")

core_data <- core_data %>%
  filter(compartment == compartment_type)
```


# ICC
```{r}
library(psych)

icc_data <- core_data %>%
  select(suid, m1_70p : neutral_4060p)
class(icc_data) <- "data.frame"

fct_icc <- function(data) {
  ICC_data <- data.frame(matrix(nrow = 1, ncol = 0))
  lb_data <- data.frame(matrix(nrow = 1, ncol = 0))
  up_data <- data.frame(matrix(nrow = 1, ncol = 0))
  for (i in 1:length(colnames(data))) {
    ids <- data %>% select(suid)

    if (class(data[, i]) == "numeric" |
        class(data[, i]) == "integer") {
      ICC_df <- cbind(ids, value = data[, i])
      ICC_df <- ICC_df %>%
        mutate(Slide = "Slide0") %>%
        group_by(suid) %>%
        mutate(n = row_number(suid)) %>%
        ungroup() %>%
        unite(slide_id, Slide:n, sep = "", remove = TRUE, na.rm = TRUE) %>%
        pivot_wider(names_from = slide_id, values_from = value
        ) %>%
        select(c(starts_with("slide")))

      ICC <- ICC(ICC_df)$results[4, 2]
      ICC_data <- cbind(ICC_data, ICC)
      ICC <- ICC(ICC_df)$results[4, 7]
      lb_data <- cbind(lb_data, ICC)
      ICC <- ICC(ICC_df)$results[4, 8]
      up_data <- cbind(up_data, ICC)

    }

  }
  ICCC_data <- bind_rows(ICC_data, lb_data, up_data)
  colnames(ICCC_data) <- colnames(data)[2:ncol(data)]
  ICCC_data <- as.data.frame(t(ICCC_data)) %>%
    mutate(ICC_lb_up = paste(round(V1, 2), " (", round(V2, 2), ", ", round(V3, 2), ")", sep = "")) %>%
    select(ICC_lb_up)
}

icc_d <-
  fct_icc(icc_data)

icc_d
```

```{r label cores}
var_label(core_data) <-
  list(refage = "Patient Age", refage_cat = "Patient Age - Categories",
       stage_cat = "Stage", histology = "Histology",
       grade = "Grade", dblkstat_CA125 = "Debulking Status",
       neutral_3070p = "Neutrals at 30/70", m1_70p = "M1 at 30/70",
       m2_30p = "M2 at 30/70", neutral_4060p = "Neutrals at 40/60",
       m1_60p = "M1 at 40/60",
       m2_40p = "M2 at 40/60",
       neutral_3070p_cat = "Neutrals at 30/70 categories", m1_70p_cat = "M1 at 30/70 categories",
       m2_30p_cat = "M2 at 30/70 categories", neutral_4060p_cat = "Neutrals at 40/60 categories",
       m1_60p_cat = "M1 at 40/60 categories",
       m2_40p_cat = "M2 at 40/60 categories"
  )
```


# VI. TAM characteristic - focus on `r compartment_type` compartment
```{r table cores}
core_data %>%
  select(m1_70p : neutral_4060p,
         m1_70p_cat : neutral_4060p_cat) %>%
  tbl_summary()
```

```{r}
core_data %>%
  select(m1_70p : neutral_4060p) %>%
  pivot_longer(cols = everything(),
               names_to = "cell_type") %>%
  mutate(cell_type =
           factor(cell_type,
                  levels = c("neutral_3070p", "m1_70p",
                             "m2_30p", "neutral_4060p",
                             "m1_60p",
                             "m2_40p"))) %>%
  ggplot(aes(x= cell_type, y= value))+
  geom_violin()+
  scale_y_log10()+
  coord_flip()
```

# VII. HR non adjusted by debulking status
## 1. Adjusted HR (**include each 3 values and use the cluster option**) - continuous
```{r}
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_4060p + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_60p + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_40p + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_3070p + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_70p + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_30p + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

## 2. Adjusted HR (**include each 3 values and use the cluster option**) - categories
```{r}
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_4060p_cat + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_60p_cat + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_40p_cat + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_3070p_cat + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_70p_cat + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_30p_cat + refage + stage_cat + histotype2,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

***
# VIII. Adjusted by debulking status
## 1. Adjusted HR (**include each 3 values and use the cluster option**) - continuous
```{r}
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_4060p + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_60p + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_40p + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_3070p + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_70p + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_30p + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

## 2. Adjusted HR (**include each 3 values and use the cluster option**) - categories
```{r}
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_4060p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_60p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_40p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ neutral_3070p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m1_70p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = core_data$os_time,
           event = core_data$os_event) ~ m2_30p_cat + refage + stage_cat + histotype2 + dblkstat_CA125,
      cluster = suid,
      data = core_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

# IX. KM
```{r}
ggsurvplot(survfit(Surv(os_time, os_event) ~ m1_60p_cat,
                   data=tam_data),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "M1 categories",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(os_time, os_event) ~ m1_70p_cat,
                   data=tam_data),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "M1 categories",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```

***









