---
title: "TAM_TMA survival analysis using marker presence/absence to categorize macrophage types"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```


```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(survival)
library(survminer)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
tam_data <- 
  read_rds(paste0(here::here(),
                  "/Clean_mapped_macrophage_data_wide_format_with_cat_09282023.rds"))

clinical <- 
  read_rds(paste0(here::here(),
                  "/case_ctrl_data_07132023.rds"))
```

```{r prep data}
tam_data <- left_join(tam_data %>% 
                         mutate(suid = as.character(suid)),
                      clinical,
                      by = "suid") %>% 
  # Remove patients that have to be excluded for AACES
  filter(!is.na(OCWAAID))

compartment_type <- "Tumor"
tam_data <- tam_data %>% 
  filter(compartment == compartment_type)

```

```{r label}
var_label(tam_data) <-
  list(refage = "Patient Age", refage_cat = "Patient Age - Categories",
       stage_cat = "Stage", histology = "Histology",
       grade = "Grade",
       m0_simple_cells = "MDSCs", m1_simple_cells = "M1",
       m2_simple_cells = "M2", m0_simple_cells_percent = "MDSCs (%)",
       m1_simple_cells_percent = "M1 (%)", 
       m2_simple_cells_percent = "M2 (%)",
       m0_simple_cells_cat = "MDSCs categories", m1_simple_cells_cat = "M1 categories",
       m2_simple_cells_cat = "M2 categories", m0_simple_cells_percent_cat = "MDSCs categories (%)",
       m1_simple_cells_percent_cat = "M1 categories (%)", 
       m2_simple_cells_percent_cat = "M2 categories (%)"
  )
```

<br>

***
<span style="color: steelblue; font-size: 40px;">Focus on `r compartment_type` compartment</span>

***
<br>

# Table 1. Patient characteristics overall

```{r}
tam_data %>% 
  # distinct(suid, .keep_all = TRUE) %>% 
  select(refage, refage_cat, 
         race, grade,
         stage_cat, histology,
         histotype1, histotype2) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # label = list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
              #              stage ~ "Stage", histology ~ "Histology"
              #              # dblkstat_CA125 ~ "Debulking Status", adj ~ "Adjuvant chemotherapy",
              #              ),
              digits = list(all_continuous() ~ 1)) %>%
      modify_header(list(label ~ "**Patient characteristics**"#, all_stat_cols() ~ "**{level}**, N = {n}"
                    )) %>%
  bold_labels()
```

* Note :  
  * M1 are pro-inflammatory anti-tumoral macrophages detected by CD86 pSTAT1 staining  
  * M2 are anti-inflammatory pro-tumoral macrophages (proliferation) detected by CD163 CD206 staining  
  * CD68 staining for TAM  

# TAM characteristic - focus on `r compartment_type` compartment
```{r cleaning}
tam_data %>% 
  select(m1_simple_cells : m0_simple_cells_percent,
         m1_simple_cells_cat : m0_simple_cells_percent_cat) %>% 
  tbl_summary()
```

```{r}
tam_data %>% 
  select(m1_simple_cells : m0_simple_cells_percent) %>% 
  pivot_longer(cols = everything(),
               names_to = "cell_type") %>% 
  mutate(cell_type = 
           factor(cell_type, 
                  levels = c("m0_simple_cells", "m1_simple_cells",
                             "m2_simple_cells", "m0_simple_cells_percent",
                             "m1_simple_cells_percent", 
                             "m2_simple_cells_percent"))) %>% 
  ggplot(aes(x= cell_type, y= value))+
  geom_violin()+
  scale_y_log10()+
  coord_flip()

tam_data %>% 
  select(suid, m1_simple_cells : m0_simple_cells) %>% 
  pivot_longer(cols = -suid,
               names_to = "cell_type") %>% 
  mutate(cell_type = 
           factor(cell_type, 
                  levels = c("m0_simple_cells", "m1_simple_cells",
                             "m2_simple_cells"))) %>% 
  ggpaired(x = "cell_type", y = "value", id = "suid",
           color = "cell_type", line.color = "gray", line.size = 0.4, point.size = 0,
           palette = "jco")+
  scale_y_log10()+
  coord_flip()

tam_data %>% 
  select(suid, m1_simple_cells_percent : m0_simple_cells_percent) %>% 
  pivot_longer(cols = -suid,
               names_to = "cell_type") %>% 
  mutate(cell_type = 
           factor(cell_type, 
                  levels = c("m0_simple_cells_percent",
                             "m1_simple_cells_percent", 
                             "m2_simple_cells_percent"))) %>% 
  ggpaired(x = "cell_type", y = "value", id = "suid",
           color = "cell_type", line.color = "gray", line.size = 0.4, point.size = 0,
           palette = "jco")+
  scale_y_log10()+
  coord_flip()
```

# Adjusted HR - continuous
```{r}
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m0_simple_cells_percent + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_simple_cells_percent + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_simple_cells_percent + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m0_simple_cells + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_simple_cells + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_simple_cells + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

# Adjusted HR - categories
```{r}
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m0_simple_cells_percent_cat + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_simple_cells_percent_cat + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_simple_cells_percent_cat + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
#
coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m0_simple_cells_cat + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m1_simple_cells_cat + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = tam_data$os_time,
                   event = tam_data$os_event) ~ m2_simple_cells_cat + refage + stage_cat,
              data = tam_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

# KM
```{r}
ggsurvplot(survfit(Surv(os_time, os_event) ~ m0_simple_cells_cat, 
                   data=tam_data),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,
           
           xlab = "Time in months",
           legend = "top",
           legend.title = "MDSCs categories",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```






