---
title: "Risk assessment AACES2 Cases Controls"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   margin-bottom: 25;
}

table {
    margin-top: 25px;
    margin-bottom: 10px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Risk assessment inflammatory-related exposures and immune cell abundance in cases controls population</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
# library(data.table)
# library(nnet)
library(gtsummary)
# library(survival)
# library(survminer)
# library(mclust)
# library(gplots)
library(fastDummies)
library(riskclustr)
```

```{r load}
markers_ROI <- readRDS(paste0(here::here(), "/summarized_markers_ROI.rds"))
case_ctrl_data <- readRDS(paste0(here::here(), "/case_ctrl_data.rds"))

# Remove these IDs from whole data because 2 are NAs in BMI and 2 are there matched
# remove_id_bmi <- paste0(c("45142", "45809", "181810", "42204"), collapse = "|")

# # Remove these IDs from peripheral ROI because 2 are NAs and 2 are there matched
# remove_id <- paste0(c("110318", "43220", "42774", "46619"), collapse = "|")
```

I removed 4 patients who don't have intratumoral ROI in the new AACES date
```{r remove patients}
# Remove these IDs with no intratumoral ROI
remove_id <- paste0(c("110362", "161094", "190155", "190176"), collapse = "|")


# ROI_global <- ROI_global %>% 
#   filter(site == "AAS") %>% 
#   filter(!str_detect(suid, remove_id))

markers_ROI <- markers_ROI %>% 
  filter(site == "AAS") %>%
  filter(!str_detect(suid, remove_id))

ctrl_data <- case_ctrl_data %>% 
  filter(site == "AAS" & casecon == "Control")
  
```

```{r create dummy var}
# Add back the control data and code dummies
ctrl_case <- bind_rows(markers_ROI, ctrl_data) %>% 
  mutate(casecon = case_when(
    casecon == "Control"                                       ~ 0,
    casecon == "Case"                                          ~ 1,
    TRUE                                                       ~ NA_real_
  )) %>% 
  mutate(across(c("cd3_total_i", "cd3_tumor_i", "cd3_stroma_i", 
                  "cd3plus_cd8plus_total_i", "cd3plus_cd8plus_tumor_i",
                  "cd3plus_cd8plus_stroma_i"), 
                ~ case_when(
                  . == "low"                                   ~ 1,
                  . == "high"                                  ~ 2,
                  is.na(.)                                     ~ 0
                ))) %>% 
  mutate(immunoscore_2018lancet_patients = case_when(
    immunoscore_2018lancet_patients == "Low"                   ~ 1,
    immunoscore_2018lancet_patients == "Intermediate"          ~ 2,
    immunoscore_2018lancet_patients == "High"                  ~ 3,
    is.na(immunoscore_2018lancet_patients)                     ~ 0
  ))

# Create dummy var for 3 level factor
ctrl_case <- dummy_cols(ctrl_case, 
                    select_columns = 
                      c("BMI_recent_grp", "BMI_YA_grp", "smokcurrent"),
                    ignore_na = FALSE) %>% 
  # remove the 0 when value is NA in the raw var
  mutate(across(c(starts_with("BMI_recent_grp_")), 
                ~ case_when(
                  is.na(BMI_recent_grp)                        ~ NA_real_,
                  TRUE                                         ~ as.numeric(.)
                ))) %>% 
  mutate(across(c(starts_with("BMI_YA_grp_")), 
                ~ case_when(
                  is.na(BMI_YA_grp)                            ~ NA_real_,
                  TRUE                                         ~ as.numeric(.)
                ))) %>% 
  # Clean colname
  `colnames<-`(str_remove_all(colnames(.), " kg/m2|-") %>% 
                 str_replace_all(., ">", "sup") %>% 
                 str_replace_all(., "<", "inf")) %>% 
  # add var
  mutate(BMI_YA_grp = case_when(
    BMI_YA < 17.6                    ~ "<17.6 kg/m2",
    BMI_YA >= 17.6 &
      BMI_YA < 25.6                  ~ "17.6-25.6 kg/m2",
    BMI_YA >= 25.6                   ~ "≥25.6 kg/m2"
  ), BMI_YA_grp = factor(BMI_YA_grp, levels = 
                           c("<17.6 kg/m2", "17.6-25.6 kg/m2", "≥25.6 kg/m2"))) %>% 
  mutate(BMI_YA_2grp = case_when(
    BMI_YA_grp == "<17.6 kg/m2" |  
    BMI_YA_grp == "17.6-25.6 kg/m2"     ~ "<25.6 kg/m2",
      BMI_YA_grp == "≥25.6 kg/m2"       ~ "≥25.6 kg/m2"
  ))

# write_rds(ctrl_case, "ctrl_case.rds")
# write_csv(ctrl_case, "risk assessment data AACES2.csv")
```

# Table
```{r}
ctrl_case %>% 
  select(BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp, 
         talcever, endomet, fibroids, pid,
         smokever, smokcurrent,
         aspirin, NSAID, aceta,
         casecon) %>% 
  tbl_summary(by= casecon,
              type = list(c(talcever, endomet, fibroids, pid, aspirin, NSAID, aceta) ~ "categorical")) %>% 
  bold_labels() %>% add_p() %>% bold_p(t= .05) %>% add_overall()
```

# Risk assessement
## Overall population
### 2 levels factor variable
```{r}
factor_name <- c("BMI_YA_2grp", "talcever", "endomet", "fibroids", "pid",
                 "smokever", "aspirin", "NSAID", "aceta")

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list(i, "refage"), 
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

#### cd3_tumor_i
```{r}
risk_ass(data = ctrl_case, type = "cd3_tumor_i")
```
#### cd3_total_i
```{r}
risk_ass(data = ctrl_case, type = "cd3_total_i")
```
#### cd3_stroma_i
```{r}
risk_ass(data = ctrl_case, type = "cd3_stroma_i")
```
#### cd3plus_cd8plus_tumor_i
```{r}
risk_ass(data = ctrl_case, type = "cd3plus_cd8plus_tumor_i")
```
#### cd3plus_cd8plus_total_i
```{r}
risk_ass(data = ctrl_case, type = "cd3plus_cd8plus_total_i")
```
#### cd3plus_cd8plus_stroma_i
```{r}
risk_ass(data = ctrl_case, type = "cd3plus_cd8plus_stroma_i")
```

### 3 levels factor variable - BMI recent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_2530", "BMI_recent_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("BMI_recent_grp_2530", "BMI_recent_grp_sup30", "refage"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

#### cd3_tumor_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_tumor_i")
```
#### cd3_total_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_total_i")
```
#### cd3_stroma_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_stroma_i")
```
#### cd3plus_cd8plus_tumor_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_tumor_i")
```
#### cd3plus_cd8plus_total_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_total_i")
```
#### cd3plus_cd8plus_stroma_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_stroma_i")
```

### 3 levels factor variable - BMI YA
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_2530", "BMI_YA_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("BMI_YA_grp_2530", "BMI_YA_grp_sup30", "refage"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

#### cd3_tumor_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_tumor_i")
```
#### cd3_total_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_total_i")
```
#### cd3_stroma_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_stroma_i")
```
#### cd3plus_cd8plus_tumor_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_tumor_i")
```
#### cd3plus_cd8plus_total_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_total_i")
```
#### cd3plus_cd8plus_stroma_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_stroma_i")
```

### 3 levels factor variable - smokcurrent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("smokcurrent_current", "smokcurrent_former", "refage"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

#### cd3_tumor_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_tumor_i")
```
#### cd3_total_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_total_i")
```
#### cd3_stroma_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3_stroma_i")
```
#### cd3plus_cd8plus_tumor_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_tumor_i")
```
#### cd3plus_cd8plus_total_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_total_i")
```
#### cd3plus_cd8plus_stroma_i
```{r}
risk_ass_bmi(data = ctrl_case, type = "cd3plus_cd8plus_stroma_i")
```
<br>
<br>

***



***


